### 2013-10-02 Rcode/test.ash.Rmd
dealt with missing data for betahat and betahatsd in computation of ZeroProb, PosteriorMean, NegativeProb

>>>>

```{r}
beta.ash=ash(ss$betahat,ss$betasd,auto=TRUE)
beta.ash.u=ash(ss$betahat,ss$betasd,mixcompdist="uniform",auto=TRUE)
beta.ash.halfu=ash(ss$betahat,ss$betasd,mixcompdist="halfuniform",auto=TRUE)
zscore = ss$betahat/ss$betasd

pval = pchisq(zscore^2,df=1,lower.tail=F)
qval = qvalue(pval)
hist(zscore)
x=seq(min(ss$beta),max(ss$beta),length=1000)
hist(ss$beta,prob=TRUE)
lines(x,density(beta.ash,x),col=2)
lines(x,density(beta.ash.u,x),col=3)
lines(x,density(beta.ash.halfu,x),col=4)
```

```{r}
#Test missing data
ss = simdata(10000,8000,0,2,1)

beta.ash=ash(c(ss$betahat,rep(NA,100)),1)
beta.ash.u=ash(c(ss$betahat,rep(NA,100)),1,mixcompdist="uniform")
beta.ash.halfu=ash(c(ss$betahat,rep(NA,100)),1,mixcompdist="halfuniform")
